\chapter{Source Code}

All the source code that has been developed for this Master Thesis is available
as a Git repository at \url{https://github.com/setzer22/master_thesis_source}.
This appendix covers the relevant parts of the project and the necessary
dependencies to build and execute it.

The repository presented consists of three main projects, divided in three
subfolders in the repository root. All three projects are built using Maven and
follow the Maven convention of folder structure: A \texttt{pom.xml} file
specifies the build instructions and dependencies, and the
\texttt{src/main/\{java,clojure\}} subfolders contain the source code for the
corresponding project.

\begin{description}
\item[\texttt{nlp4bpm\_commons}]{This project contains several utilities that
    are used across atdlib and all the algorithms of the \emph{NLP4BPM} project.
    The relevant source files for this project are \texttt{freeling\_api.clj} and
    \texttt{Freeling.clj}, which wrap FreeLing's JNI interface and
    \texttt{label\_parser.clj} which implements the custom SRL module for BPMN
    labels described in Section~\ref{sec:process_model_analysis}.}
\item[\texttt{atdlib}]{ATDlib implements all functionalities described in
    Chapter~\ref{cha:atdlib}. The source file names correspond to the same
    module names used in this document and thus should be self-explanatory.}
\item[\texttt{modeljudge}]{This project contains the implementation for the
    \emph{Model Judge} algorithm. The major part of this module consists of an
    adaptation of the alignment between textual descriptions and BPMN process
    models. The parts that are specific to \emph{Model Judge} are in the
    \texttt{core\_students.clj} namespace.}
\end{description}

To build some of the projects, some Java dependencies not available in any maven
repository must be included. These are distributed inside the \texttt{jars}
folder of the relevant project, with a bash script that installs them into the
local Maven repository. Additionally, there are two native dependencies that
cannot be bundled into the project due to size and/or license restrictions:
FreeLing 4.0 or
higher\footnote{http://nlp.lsi.upc.edu/freeling/index.php/node/30} and the
Gurobi ILP solver\footnote{http://www.gurobi.com/downloads/download-center}.
Please note that Gurobi requires an academic or commercial license. These must
be installed in the target system and listed in the system's \texttt{PATH} and
\texttt{LD\_LIBRARY\_PATH} variables (or the equivalent in Windows operating
systems).